---
title: PSY 8960 Week 8 Project 
author: Chulin Chen
output: html_document
date: "2023-03-14"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../out") })
---
# Reproducible Image and Online Resources
An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](https://mybinder.org/v2/gh/ChulinChen20/psy8960-week8.git/HEAD).

An interactive web app is available by [clicking this link instead](https://chulinchen23.shinyapps.io/shiny_week8/).

# Script Settings and Resources
Set the working directory to where the RMarkdown File is in, load all the necessary packages, and suppress outputs. message=FALSE is used as the only output is the meassage from tidyverse.
```{r setup, message=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(ggplot2)
library(tidyverse)
```

# Data Import and Cleaning
Import dataset, convert the reversed coded variable q5, and convert variables to types appropriate for later analysis.
```{r}
week8_tbl <-read_csv("../data/week3.csv",col_types=cols(timeStart=col_datetime(format="%Y-%m-%d %H:%M:%S"))) %>%
  mutate(q5=6-q5) %>%
  mutate(condition= factor(condition, levels = c("A","B","C"),labels=c("Block A","Block B","Control"))) %>%
  mutate(gender= factor(gender, levels = c("M","F"),labels=c("Male","Female")))%>%
  mutate(timeStart = ymd_hms(timeStart)) %>%
  mutate(mean1 = rowMeans(across(q1:q6)),
         mean2 = rowMeans(across(q8:q10))) %>%
  mutate(after_aug2017 = timeEnd > "2017-08-01 00:00:00")
```

# Visualization
Display a table of data in q1-q6 using the package DT as it creates paginated tables. Create a scatterplot between mean scores on Q1-Q6 (x-axis) and mean scores on Q8-Q10 (y-axis), relabel axes for clearer presentation.
```{r, echo=FALSE}
select(week8_tbl, paste0("q",1:6))

week8_tbl %>%
  rowwise() %>%
  ggplot(aes(mean1,mean2)) +
  geom_point() +
  geom_smooth(method="lm", color = "purple") +
  labs(x="mean scores on Q1-Q6",y="mean scores on Q8-Q10")
```

# Analysis
Display output summarizing the correlation between the two mean scores. 
```{r}
cor.test(week8_tbl$mean1, week8_tbl$mean2)
```
The correlation coefficient is `r cor.test(week8_tbl$mean1, week8_tbl$mean2)$estimate`. Assuming that the alpha level is 0.05, as the p-value is greater than 0.05, the correlation is not significant.

# Data Export
Export data to a skinny RDS format data as it is most suitable for shiny app. Save the data to a folder containing the app.
```{r}
week8_tbl %>%
  select(mean1, mean2, 
         gender, after_aug2017) %>%
  saveRDS("../shiny_week8/shiny_skinny.RDS")
```

















