---
title: PSY 8960 Week 8 Project 
author: Chulin Chen
output: html_document
date: "2023-03-14"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../out") })
---

**Reproducible Image and Online Resources**
An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](https://mybinder.org/v2/gh/ChulinChen20/psy8960-week8.git/HEAD).
An interactive web app is available by [clicking this link instead](https://chulinchen23.shinyapps.io/shiny/).

**Script Settings and Resources**
Set the working directory to where the RMarkdown File is in, load all the necessary packages, and suppress outputs.
```{r setup, message=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(ggplot2)
library(tidyverse)
library(DT)
```

**Data Import and Cleaning**
Import dataset, convert the reversed coded variable q5, and convert variables to types appropriate for later analysis.
```{r}
week8_tbl <-read_csv("../data/week3.csv",col_types=cols(timeStart=col_datetime(format="%Y-%m-%d %H:%M:%S"))) %>%
  mutate(q5=6-q5) %>%
  mutate(condition= factor(condition, levels = c("A","B","C"),labels=c("Block A","Block B","Control"))) %>%
  mutate(gender= factor(gender, levels = c("M","F"),labels=c("Male","Female")))%>%
  mutate(timeStart = ymd_hms(timeStart))
```

**Visualization**
Display a table of data in q1-q6 and a scatterplot between mean scores on Q1-Q6 (x-axis) and mean scores on Q8-Q10 (y-axis).
```{r, echo=FALSE}
DT::datatable(week8_tbl[,paste0("q",1:6)])

week8_tbl %>%
  rowwise() %>%
  mutate(mean1 = mean(q1:q6),
         mean2 = mean(q8:q10)) %>%
  ggplot(aes(mean1,mean2)) +
  geom_point() +
  geom_smooth(method="lm", color = "purple") +
  labs(x="mean scores on Q1-Q6",y="mean scores on Q8-Q10")
```

**Analysis**
Display output summarizing the correlation between the two mean scores. Calculate the two means first and then create two new variables to store correlation coefficient and p-value.
```{r}
correlation <- week8_tbl %>%
  rowwise() %>%
  mutate(mean1 = mean(q1:q6),
         mean2 = mean(q8:q10)) %>%
  unnest(cols=c(mean1,mean2)) %>%
  summarize(coef=cor.test(mean1,mean2)$estimate,
            p_value = cor.test(mean1,mean2)$p.value)

correlation
```
The correlation coefficient is `r correlation$coef`. Assuming that the alpha level is 0.05, as the p-value is greater than 0.05, the correlation is not significant.

**Data Export**
```{r}
saveRDS(week8_tbl, "../shiny/week8_tbl")
```

